Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-04-14 article_springer/article_springer.Rmd
Change abstract, third person

- name: "Katharina Hees"
  affiliation: a
  email: "hees@statistik.tu-dortmund.de"

@@

  This article proposes a new model for the _inter-exceedance times_ of events 
  above high thresholds; the threshold exceedances itself are modeled via the standard 
  Peaks-Over-Threshold (POT) method. For high thresholds and 
  infinite-mean waiting times, we show that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process of threshold
  exceedances.
  We provide graphical means of estimating model parameters and assessing 
  model fit. Along the way, we apply our inference method to a real-world
  bursty time series, and 
  show how the memory of the Mittag-Leffler distribution affects 
  the predictive distribution for the time until the next extreme event.

>>>>

- name: "Katharina Hees"
  affiliation: a
  email: "hees@statistik.tu-dortmund.de"
  correspondence: true

@@

  A new model for the _inter-exceedance times_ of events 
  above high thresholds is proposed; the threshold exceedances itself are modeled via the standard 
  Peaks-Over-Threshold (POT) method. For high thresholds and 
  infinite-mean waiting times, it is shown that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process of threshold
  exceedances.
  Graphical means of estimating model parameters and assessing 
  model fit are provided. Along the way, the inference method gets applied to a real-world
  bursty time series, and it is shown how the memory of the Mittag-Leffler distribution affects 
  the predictive distribution for the time until the next extreme event.
